Combining information from photometric and spectroscopic data:\\ Probabilistic spectrophotometric inference

### 2015-06-16 tex/figures.tex
clean up plotting scripts

\begin{figure}[h!]
%\includegraphics[width = 0.5 \textwidth]{figures/dfig_b192-g242_020.png}
\caption{A mock spectrum for a star cluster with the fiducial
parameters $10^5 M_\odot$ total stellar mass, an age of 9 Gyr, solar
metallicity, and $A_V=0.5$ mag. \label{fig:mock_data}}
\end{figure}

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/ideal.pdf}
\caption{Results of inference from a mock spectrum and a single
  photometric data point where the spectrophotometric calibration is
  assumed to be perfectly known. 
Top Left: The mock observed spectrum ({\it black}) is shown as well as
YY model spectra constructed from draws from the posterior PDFs of the
model parameters.
Bottom Right: Marginalized posterior PDFs for several of the physical
parameters of interest.  The input mock parameters are shown as
vertical black lines.
{\color{red} Remove calibration plot and intrinsic plot, since it is
  the same as observed spectrum.  Show residuals.}
\label{fig:speconly_ideal}}
\end{figure*}

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/speconly_calibrated.pdf}
\caption{Results of inference from a \emph{perfectly calibrated} mock
  spectrum and a single photometric data point, where uncertainties in
  the calibration are modeled.
Top Left: The mock observed spectrum ({\it black}) is shown as well as
YY model spectra constructed from draws from the posterior PDFs of the
model parameters, including calibration parameters {\it green}.
Bottom Left: In this case the true calibration vector ({\it black}) is a constant.
Posterior samples of the inferred calibration vector ({\it green}) include both
the polynomial and the Gaussian Process mean prediction (Equation
\ref{eq:calibration}).
Top Right: Samples of the posterior prediction for the
\emph{intrinsic} spectrum ({\it green}) as well as for the photometry
({\it magenta}).  The true mock photometry is also shown ({\it
black}).
Bottom Right: Marginalized posterior PDFs for several of the physical
parameters of interest.  The input mock parameters are shown as
vertical lines.
 {\color{red} This is not converged.  mass and dust2 PDFs will become
   much broader.}
\label{fig:speconly_calibrated}}
\end{figure*}

@@

\begin{figure*}[h!]
\includegraphics[width=0.5 \textwidth]{figures/photonly.pdf}
\caption{Results of inference from the photometric data only.  The
  redshift is fixed {\color{blue} (should just use a tight prior)} and
 spectroscopic calibration parameters are not modeled.
Top: The intrinsic spectrum. Samples of the posterior prediction
for the \emph{intrinsic} spectrum ({\it green}) and the
photometry ({\it magenta}).  The mock photometry is also shown
({\it black}).
Right: Marginalized posterior PDFs for several of the physical
parameters of interest.  The input mock parameters are shown as
vertical lines.
\label{fig:photonly}}
\end{figure*}

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/specphot_uncalibrated.pdf}
\caption{Results of inference from the combination of
  \emph{uncalibrated} spectroscopy and all the photometric data
  points.  Panels and colors are as in Figure \ref{fig:speconly_calibrated}.
\label{fig:specphot_uncalibrated}}
\end{figure*}

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/combined_post.pdf}
\caption{Joint posterior PDFs for several physical parameters. The
posteriors obtained from photometry only are in {\it red}, from
\emph{uncalibrated} spectroscopy and a single photometric point in
{\it blue}, and from the photometry and spectroscopy combined in {\it
magenta}.  The contours are 1 and 2-sigma contours. The true values
are indicated by {\it black points}.
\label{fig:combined_posterior}}
\end{figure*}

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/noise_realizations.pdf}
\caption{Percentiles of the posterior PDFs for four of the parameters,
  obtained from multiple noise realizations of the
  mock photometry and uncalibrated spectra.  The input mock parameters are shown as a 
 black horizontal line, The red shaded region gives the 16th to 84th percentile
 range for a noiseless mock.
\label{fig:noise_realizations}}
\end{figure*}

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/vary_params.pdf}
\caption{Offset from the input parameters of the medians of the
posterior PDFs for  inference from mock spectra and
photometry, as a function of the mock parameter that is varied.
 \label{fig:mock_parameter_space}}
\end{figure*}

@@

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/vary_nphot.png}
\caption{Inference from a real, calibrated, spectrum.  Top left:
  Observed spectrum and posterior samples thereof.  Bottom left:
  residuals.  Top right: inferred calibration vector, samples.
  Bottom right: posterior PDFs (corner plot?) for physical parameters.
\label{fig:real_calibrated}}
\end{figure*}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/vary_nphot.png}
\caption{Inference from a real, uncalibrated, spectrum.  Top left:
  Observed spectrum and posterior samples thereof.  Bottom left:
  residuals.  Top right: inferred calibration vector, samples.
  Bottom right: posterior PDFs (corner plot?) for physical parameters.
\label{fig:real_uncalibrated}}
\end{figure*}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/vary_nphot.png}
\caption{Ratio of the calibration vector inferred from the
  real uncalibrated spectrum to that inferred from the real calibrated
  spectrum ({\it green}). Taking the ratio reduces the effects of model
  imperfections and shows how well we are able to infer the
  calibration vector of \citet{schiavon05} ({\it black}).  
\label{fig:real_calibration_ratio}}
\end{figure*}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/vary_nphot.png}
\caption{Inferred parameters for \excluster.  We show the inference from the
  calibrated spectrum ({\it red}), from the uncalibrated spectrum
  ({\it blue}), and from the CMD ({\it black}).
\label{fig:real_parameters}}
\end{figure*}

>>>>

\begin{figure*}[h!]
\includegraphics[width=0.5 \textwidth]{figures/ideal.pdf}
\caption{Results of inference from a mock spectrum and a single
  photometric data point where the spectrophotometric calibration is
  assumed to be perfectly known. 
Top: Model spectra ({\it green}) and photometry ({\it orange})
constructed from draws from the posterior PDFs of the model
parameters, compared to the true intrinsic spectroscopy and photomtry
({\it black})
Bottom: Marginalized posterior PDFs for several of the physical
parameters of interest.  The input mock parameters are shown as
vertical black lines.
{\color{red} Show residuals.}
\label{fig:speconly_ideal}}
\end{figure*}

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/speconly_calibrated.pdf}
\caption{Results of inference from a \emph{perfectly calibrated} mock
  spectrum and a single photometric data point, where uncertainties in
  the calibration are modeled.
Top Left: The uncertainty normalized residuals between the mock
observed spectrum ({\it black}) and YY model spectra constructed from
draws from the posterior PDFs of the model parameters, including
calibration parameters {\it blue}.
Bottom Left: In this case the true calibration vector ({\it black}) is a constant.
Posterior samples of the inferred calibration vector ({\it blue}) include both
the polynomial and the Gaussian Process mean prediction (Equation
\ref{eq:calibration}).
Top Right: Samples of the posterior prediction for the
\emph{intrinsic} spectrum ({\it blue}) as well as for the photometry
({\it orange}).  The true mock photometry is also shown ({\it
black}).
Bottom Right: Marginalized posterior PDFs for several of the physical
parameters of interest.  The input mock parameters are shown as
vertical lines.
 {\color{red} This is not converged.  mass and dust2 PDFs will become
   much broader.}
\label{fig:speconly_calibrated}}
\end{figure*}

@@

\begin{figure*}[h!]
\includegraphics[width=0.5 \textwidth]{figures/photonly.pdf}
\caption{Results of inference from the photometric data only.  The
  redshift is fixed {\color{blue} (should just use a tight prior)} and
 spectroscopic calibration parameters are not modeled.
Top: The intrinsic spectrum. Samples of the posterior prediction
for the \emph{intrinsic} spectrum ({\it red}) and the
photometry ({\it orange}).  The mock photometry is also shown
({\it black}).
Right: Marginalized posterior PDFs for several of the physical
parameters of interest.  The input mock parameters are shown as
vertical lines.
\label{fig:photonly}}
\end{figure*}

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/specphot_uncalibrated.pdf}
\caption{Results of inference from the combination of
\emph{uncalibrated} spectroscopy and all the photometric data points.
Panels and are as in Figure \ref{fig:speconly_calibrated}.
\label{fig:specphot_uncalibrated}}
\end{figure*}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/specphot_uncalibrated.pdf}
\caption{Joint Posterior PDFs for the calibration parameters inferred
from the combination of \emph{uncalibrated} spectroscopy and all the
photometric data points.
\label{fig:cal_posterior}}
\end{figure*}

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/combined_post.pdf}
\caption{Corner plot of joint and marginal posterior PDFs for several
physical parameters. The posteriors obtained from photometry only are
in {\it red}, from \emph{uncalibrated} spectroscopy and a single
photometric point in {\it blue}, and from the photometry and
spectroscopy combined in {\it magenta}.  The contours are 1 and
2-sigma contours. The true values are indicated by {\it black points}.
\label{fig:combined_posterior}}
\end{figure*}

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/noise_realizations.pdf}
\caption{Percentiles of the posterior PDFs for four of the parameters,
obtained from multiple noise realizations of the mock photometry and
uncalibrated spectra.  The input mock parameters are shown as a black
horizontal line, The green shaded region gives the 16th to 84th
percentile range for a noiseless mock.
\label{fig:noise_realizations}}
\end{figure*}

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/vary_params.pdf}
\caption{Offset of the posteriors from the input parameters for
inference from mock spectra and photometry, as a function of the mock
parameter that is varied.  The medians of the posterior PDFs are shown
as connected black circles, the 16th and 84th percentile of the
posteriors are indicated by the gray shaded region.
Left: Results when varying age.
Middle: Results when varying metallicity.
Right: Results when varying dust attenuation.
 \label{fig:mock_parameter_space}}
\end{figure*}

@@

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/real_calibrated.pdf}
\caption{Inference from a real, \emph{calibrated}, spectrum. 
 Top left: Residuals.  
Bottom left: Inferred calibration vactor.  
Top right: Inferred instrinsic SED.
Bottom right: posterior PDFs for selected physical parameters.
\label{fig:real_calibrated}}
\end{figure*}

\begin{figure*}[h!]
\includegraphics[width=\textwidth]{figures/real_uncalibrated.pdf}
\caption{Inference from a real, \emph{uncalibrated}, spectrum.   
Top left: Residuals.  
Bottom left: Inferred calibration vactor.  
Top right: Inferred instrinsic SED.
Bottom right: posterior PDFs for selected physical parameters.
\label{fig:real_uncalibrated}}
\end{figure*}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/inferred_calibration.pdf}
\caption{Left: Ratio of the calibration vector inferred from the
  real uncalibrated spectrum to that inferred from the real calibrated
  spectrum ({\it green}). Taking the ratio reduces the effects of model
  imperfections and shows how well we are able to infer the
  calibration vector of \citet{schiavon05} ({\it black}).  
Right: Joint posterior PDFs for the inferred calibration parameters.
\label{fig:real_calibration_ratio}}
\end{figure*}

\begin{figure*}[h!]
%\includegraphics[width=\textwidth]{figures/real_phys_posterior.png}
\caption{Inferred parameters for \excluster.  We show the inference from the
  calibrated spectrum ({\it red}), from the uncalibrated spectrum
  ({\it blue}), and from the CMD ({\it black}).
\label{fig:real_parameters}}
\end{figure*}

### 2015-06-16 tex/ms.tex
clean up plotting scripts

XXX logarithmic Alternative XXX
In this case we define the residual of the data from the model in
terms of the logarithmic differences.  This logarithmic formulation
requires that $d$ be everywhere positive, and distorts the
uncertainties, especially at low S/N ratio.  The advantages of
defining the residual in this way are that the model remains linear
(and therefore fast) and the calibration vector is forced to be
positive everywhere.  Additionally, at high signal to noise the
distortion of the uncertainties will be minimal.

The calibration-vector and Gaussian-Process modified log-likelihood is
\begin{eqnarray}\label{eq:spectroscopicLF}
\ln p(d\given\theta,\alpha) &=&
                                -\frac{1}{2}\,\left[\transpose{\Delta}\,C^{-1}\,\Delta
                                + \ln([2\pi]^N\,\det{C}) \right]
\\
\Delta &\equiv& \ln d - \ln \mu(\theta) - \ln f(\alpha) 
\\
C_{nn'} &\equiv& [\hat{\sigma}_n^2 + s^2]\,\delta_{nn'} +
K_\alpha(\lambda_n - \lambda_{n'})
\\
\hat{\sigma_n} & = &\sigma_n/d
\quad ,
\end{eqnarray}
where $\hat{\sigma}_n$ are the fractional uncertainties of the data.
The residual column vector is defined in terms of the logarithmic
difference between the data and the mean model $\mu$ since we are
taking the calibration vector to be multiplicative with respect to the
mean model $\mu$. In this formulation the the mean model $\mu$ will be
effectively multiplied by $e ^{f(\alpha)}$

@@

\subsection{Mock Data}
Our mock data are designed to mimic the actual data as much as
possible.  Mock spectra and photometry are generated from the model
described in below (\S\ref{sec:cluster_model}, equation
\ref{eq:StarModel}) for a given set of parameters $\theta_s$.  We then
convolve the spectrum with an instrumenal LSF, interpolate onto the
observed wavelength scale and add noise according to the SNR of the
real data.  For the photometry we assume a SNR of 10.  We also mask
the mock spectra at the location of significant sky lines and ISM
lines that are present in the real data.

We will refer to these spectra as the \emph{perfectly calibrated} mock
spectrum.  An example is shown in Figure \ref{fig: mock data}. We also
produce mock spectra by dividing the perfectly calibrated spectra by
the spectrophotometric calibration vector taken from the real data
\citep[][Fig\ref{fig:ggc_spectrum}]{schiavon05}.  We refer to these as
the \emph{uncalibrated} mock spectra.

>>>>

%XXX logarithmic Alternative XXX
%In this case we define the residual of the data from the model in
%terms of the logarithmic differences.  This logarithmic formulation
%requires that $d$ be everywhere positive, and distorts the
%uncertainties, especially at low S/N ratio.  The advantages of
%defining the residual in this way are that the model remains linear
%(and therefore fast) and the calibration vector is forced to be
%positive everywhere.  Additionally, at high signal to noise the
%distortion of the uncertainties will be minimal.

%The calibration-vector and Gaussian-Process modified log-likelihood is
%\begin{eqnarray}\label{eq:spectroscopicLF}
%\ln p(d\given\theta,\alpha) &=&
%                                -\frac{1}{2}\,\left[\transpose{\Delta}\,C^{-1}\,\Delta
%                                + \ln([2\pi]^N\,\det{C}) \right]
%\\
%\Delta &\equiv& \ln d - \ln \mu(\theta) - \ln f(\alpha) 
%\\
%C_{nn'} &\equiv& [\hat{\sigma}_n^2 + s^2]\,\delta_{nn'} +
%K_\alpha(\lambda_n - \lambda_{n'})
%\\
%\hat{\sigma_n} & = &\sigma_n/d
%\quad ,
%\end{eqnarray}
%where $\hat{\sigma}_n$ are the fractional uncertainties of the data.
%The residual column vector is defined in terms of the logarithmic
%difference between the data and the mean model $\mu$ since we are
%taking the calibration vector to be multiplicative with respect to the
%mean model $\mu$. In this formulation the the mean model $\mu$ will be
%effectively multiplied by $e ^{f(\alpha)}$

@@

\subsection{Mock Data}
Our mock data are designed to mimic the actual data as much as
possible.  Mock spectra and photometry are generated from the model
described in below (\S\ref{sec:cluster_model}, equation
\ref{eq:StarModel}) for a given set of parameters $\theta_s$.  We then
convolve the spectrum with an instrumenal LSF, interpolate onto the
observed wavelength scale and add noise according to the SNR of the
real data.  We also mask the mock spectra at the location of
significant sky lines and ISM lines that are present in the real data.
For the mock photometry we assume a SNR of 10.

We will refer to these spectra as the \emph{perfectly calibrated} mock
spectrum. We also produce mock spectra by dividing the perfectly
calibrated spectra by the spectrophotometric calibration vector taken
from the real data \citep[][Fig\ref{fig:ggc_spectrum}]{schiavon05}.
We refer to these as the \emph{uncalibrated} mock spectra.
